A Linear Regression Model for Predicting MSDN Forums Votes

### 2018-11-02 forums/postScraping/msdn.forums.rmd
rmd

@@

```{r echo=FALSE, message=FALSE, warning=FALSE}
plot(vcrcv, col=forums$threadState)
```

>>>>

#plot(forums, col=forums$threadState)

library(psych)
pairs.panels(forums, lm = TRUE,
             method = "pearson", # correlation method
             hist.col = "#00AFBB",
             density = TRUE,  # show density plots
             ellipses = TRUE # show correlation ellipses
             )
```

@@

```{r echo=FALSE, message=FALSE, warning=FALSE}
#plot(vcrcv, col=forums$threadState)

library(psych)
pairs.panels(forums, lm = TRUE, pch=21, cex.cor=1, smooth=TRUE, stars=TRUE,
             method = "pearson", # correlation method
             hist.col = "#00AFBB",
             density = TRUE,  # show density plots
             ellipses = TRUE # show correlation ellipses
)
```
